Commit Rater

### 2015-08-26 presentations/paper/conclusion.tex
Add Future Work

>>>>

The implementation and concepts presented in this paper are, due to the scope of the MSR course they were made in, largely prototypical and could be improved upon in several way.

Firstly, the internal threats to validity presented in section \ref{sec:internal-threats} could largely be resolved by replacing the criteria used to synthesize data, or by improving their implementation to more accurately represent their abstract idea.

Furthermore, a nicer interface could be provided to users of the web application. Comparisons could be drawn to other authors or repositories, better suggestions for improvement could be implemented and graphs could be used to visualize the results.

Finally, language-specific criteria could be implemented as well. This would make the Commit Rater much more powerful, as it would be able to also analyze the contents of each commit. For example, it could recognize bad practices such as commented-out code or mixed whitespace and non-whitespace changes.
